Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-10 ms.tex
spell checker
spelling

This paper is organized as follows.  In $\S\ref{sec:model}$ we
describe our model, including the sample of galaxy properties used in
our analysis ($\S\ref{sec:gal_model}$) and our numerical procedure for
calculating the steady-state hydrodynamic profile of the CNM
($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
analytic results, which are justified via the numerical solutions we
present in $\S\ref{sec:numerical}$.  We move from a general and
parametrized treatment of heating to a physically motivated one in \S
\ref{sec:heating}, where we consider a range of physical processes
that can inject energy into the CNM.  In $\S\ref{sec:discussion}$ we
discuss the implications of our results for topics which include the
nuclear X-ray luminosities of quiescent black holes, jetted TDEs, and
the growth of SMBHs in the local universe.  In
$\S\ref{sec:conclusions}$ we summarize our conclusions.  Table
\ref{table:definitions} provides the definitions of commonly used
variables.  Appendices \ref{app:rs} and \ref{app:be} provide useful
analytic results for the stagnation radius and the Bernoulli parameter
of the flow, while Appendix \ref{app:windheat} provides the details of
our method for calculating stellar wind heating and mass input.

@@

\item Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the SFH in the galactic nuclear region.  A young starburst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for exclusively old stellar populations  mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.  Ongoing, continuous star formation presents a hybrid situation, with energy input usually dominated by young stars and mass input dominated by the old stars (Appendix \ref{app:windheat}).  Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs (as derived from cosmological simulations) receive a stellar wind heating of $v_w \sim 700$ km s$^{-1}$.  This heating can be suppressed if the star formation is sufficiently intermittent (Fig.~\ref{fig:NickPlot2}).

@@

\item Low mass black holes grow in the low redshift universe over
  timescales comparable to the Hubble time (\citet{Heckman+04}).  This
  accretion rates so required are too high to be consistent with the
  value predicted for the average SFH history and the maximum allowed
  for steady-state, thermally stable accretion
  (Fig.~\ref{fig:bh_growth}).  Low-$M_{\bullet}$ growth and AGN
  activity must instead be driven by a supply of gas external to the
  nucleaus, e.g. due to galaxy mergers or thermal instabilities on
  larger, galactic scales (e.g.~\citealt{Voit+15}).

@@

On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
      (generally unresolved) emission in excess of the inward
      extrapolation of the Nuker law.  They note that these nuclei are bluer
      than the background galaxy starlight, suggesting the presence of
      younger stars towards galactic centre {\bf AG mass
        threshold for this effect}.  Mass injection to the nucleus could in some cases therefore be dominated by a nuclear star cluster with its own break radius on parsec scales, i.e. much smaller than our fiducial value of $r_b \sim 100$ pc.  In the case of high heating, a smaller break radius does not appreciably change the stagnation radius, resulting in a similar SMBH accretion rate.  For break radii smaller than the nominal stagnation radius, the presence of a smaller break radius would likely decrease the stagation radius and accretion rate.  
%      be for large break radii, the stagnation radius would move
 %     inwards somewhat. However note the for high heating rate ($v_w
  %    \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
   %   \Msun$), we predict stagnation radii smaller than a parsec.

>>>>

This paper is organized as follows.  In $\S\ref{sec:model}$ we
describe our model, including the sample of galaxy properties used in
our analysis ($\S\ref{sec:gal_model}$) and our numerical procedure for
calculating the steady-state hydrodynamic profile of the CNM
($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
analytic results, which are justified via the numerical solutions we
present in $\S\ref{sec:numerical}$.  We move from a general and
parameterized treatment of heating to a physically motivated one in \S
\ref{sec:heating}, where we consider a range of physical processes
that can inject energy into the CNM.  In $\S\ref{sec:discussion}$ we
discuss the implications of our results for topics which include the
nuclear X-ray luminosities of quiescent black holes, jetted TDEs, and
the growth of SMBHs in the local universe.  In
$\S\ref{sec:conclusions}$ we summarize our conclusions.  Table
\ref{table:definitions} provides the definitions of commonly used
variables.  Appendices \ref{app:rs} and \ref{app:be} provide useful
analytic results for the stagnation radius and the Bernoulli parameter
of the flow, while Appendix \ref{app:windheat} provides the details of
our method for calculating stellar wind heating and mass input.

@@

\item Stellar wind heating, supernovae, and AGN feedback depend explicitly on the SMBH mass as well as the SFH in the galactic nuclear region.  A young starburst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for exclusively old stellar populations  mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.  Ongoing, continuous star formation presents a hybrid situation, with energy input usually dominated by young stars and mass input dominated by the old stars (Appendix \ref{app:windheat}).  Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ heated according to their average SFHs (as derived from cosmological simulations) receive a stellar wind heating of $v_w \sim 700$ km s$^{-1}$.  This heating can be suppressed if the star formation is sufficiently intermittent (Fig.~\ref{fig:NickPlot2}).

@@

\item Low mass black holes grow in the low redshift universe over
  timescales comparable to the Hubble time (\citet{Heckman+04}).  This
  accretion rates so required are too high to be consistent with the
  value predicted for the average SFH history and the maximum allowed
  for steady-state, thermally stable accretion
  (Fig.~\ref{fig:bh_growth}).  Low-$M_{\bullet}$ growth and AGN
  activity must instead be driven by a supply of gas external to the
  nucleus, e.g. due to galaxy mergers or thermal instabilities on
  larger, galactic scales (e.g.~\citealt{Voit+15}).

@@

On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
      (generally unresolved) emission in excess of the inward
      extrapolation of the Nuker law.  They note that these nuclei are bluer
      than the background galaxy starlight, suggesting the presence of
      younger stars towards galactic center {\bf AG mass
        threshold for this effect}.  Mass injection to the nucleus could in some cases therefore be dominated by a nuclear star cluster with its own break radius on parsec scales, i.e. much smaller than our fiducial value of $r_b \sim 100$ pc.  In the case of high heating, a smaller break radius does not appreciably change the stagnation radius, resulting in a similar SMBH accretion rate.  For break radii smaller than the nominal stagnation radius, the presence of a smaller break radius would likely decrease the stagnation radius and accretion rate.  
%      be for large break radii, the stagnation radius would move
 %     inwards somewhat. However note the for high heating rate ($v_w
  %    \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
   %   \Msun$), we predict stagnation radii smaller than a parsec.
